### 2014-11-03 paper/main.tex
added figure on good and poor measurements to paper

@@

Another method for FDR estimation, and perhaps the one most closely related to our
work here, is due to \cite{muralidharan.xx}, implemented in the R package \mixfdr.
Like \locfdr, \mixfdr works with $z$ scores, but it differs in that it {\it explicitly} models the alternative
distribution of $z$ scores (using a mixture of normal distributions). In principle this approach also differs from \qvalue and \locfdr in
that it does not explicitly make the Zero Assumption. However, the fitting procedure used means that the approach often comes close to making the ZA in practice.

@@

Mention correspondance between fdr and FDR?

@@

\begin{figure}
\center \includegraphics[height=6in]{Rcode/figures/decomp_ZA.pdf}
\caption{Comparison of the way that different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (light blue). In the $z$ score space the alternative distribution is placed on the bottom to make its shape easy to see.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) assumes that the effect sizes (and thus the $z$ scores) have a unimodal distribution about 0, resulting in a very different decomposition that in this case is much closer to the truth. (These data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything light blue.)} \label{fig:ZA}
\end{figure}

@@

To give a concrete example, we performed a simple simulation in which half the observations have
good precision ($s_j = 0.5$) and half the observations have very poor precision ($s_j=10$). In both cases,
we assume that half the effects are null ($\beta_j=0$)
and the other half are normally distributed with standard deviation 2 ($\beta_j \sim N(0,2)$). 
That is, we simulate $\beta_j$ from a mixture 
\begin{equation}
p(\beta) = 0.5 \delta_0(\beta) + 0.5 N(\beta; 0,2)
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0.

>>>>

Mention correspondance between fdr and FDR?
Tidy to deal with fact that definitions I give here implicitly assume $\fdr(t)$ etc don't depend on $j$.
Mention that Frequentist and Bayesian alignment depends on assumptions?

@@

Another method for FDR estimation, and perhaps the one most closely related to our
work here, is due to \cite{muralidharan.xx}, implemented in the R package \mixfdr.
Like \locfdr, \mixfdr works with $z$ scores, but it differs in that it {\it explicitly} models the alternative
distribution of $z$ scores (using a mixture of normal distributions). In principle this approach also differs from \qvalue and \locfdr in
that it does not explicitly make the Zero Assumption. However, we have found that in practice the results often approximately satisfy the ZA,
which we believe to be due to details in the fitting procedure used.

@@

@@

\begin{figure}
\center \includegraphics[height=6in]{Rcode/figures/decomp_ZA.pdf}
\caption{Comparison of the way that different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (light blue). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) assumes that the effect sizes (and thus the $z$ scores) have a unimodal distribution about 0, resulting in a very different decomposition that in this case is much closer to the truth. (These data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything light blue.)} \label{fig:ZA}
\end{figure}

@@

To give a concrete example, we performed a simple simulation in which half the observations have
reasonably good precision ($s_j = 1$) and half the observations have very poor precision ($s_j=10$). In both cases,
we assume that half the effects are null ($\beta_j=0$)
and the other half are normally distributed with standard deviation 1 ($\beta_j \sim N(0,1)$). 
That is, we simulate $\beta_j$ from a mixture 
\begin{equation}
p(\beta) = 0.5 \delta_0(\beta) + 0.5 N(\beta; 0,1)
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0.

\begin{figure}
\center \includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_hist.pdf}
\caption{Illustration of the way that high-noise observations can contaminate signal from low-noise observations.} \label{fig:GOODPOOR}
\end{figure}
